Capstone Movielens Report

### 2025-11-22 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: model.tune.param_range.

#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) Function {#func.model.tune.param_range}
\

@@

The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) is available in the [Model Tuning](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L78) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L198) script on _GitHub_.
:::

>>>>

#### [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) Function {#func.model.tune.param_range}
\

@@

The complete source code of the [model.tune.param_range](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) is available in the [Regularization](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L69) section of the [common-helper.functions.R](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/support-functions/common-helper.functions.R#L208) script on _GitHub_.
:::
